%\the\textwidth = 379.37pt

\chapter{Preliminaries}
%Related research
\label{chap:preliminaries}
\minitoc

\thispagestyle{empty}

\newpage
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{sec:2_intro}}
\lettrine[lines=4]{\color{brickred}T}{his} chapter briefly introduces the fundamental theories which are employed in the development of this thesis, i.e. the ones of \textit{port--Hamiltonian systems} and \textit{hybrid dynamical systems}. The inclusion of this Chapter in this thesis is justified by the need of smoothly introducing the reader -- which might not be an expert on control theory -- to the very basic concepts which will be used intensively in the rest of the manuscript.
Firstly, the concept of Lyapunov stability and passivity are recalled together with some of the properties of passive system, e.g. output feedback stabilization.
%
\newline

%
Secondly, the input--state--output model of a port--Hamiltonian (PH) system is defined. Then, it is shown how the power balance equation, derived from the model, highlights the most important properties of this framework. Three modeling examples are provided to give a physical and practical meaning to the theory. The first two examples are related to the dynamics of mechanical systems while the third one is taken from mathematical biology, proving the generality of the PH framework.   
The passivity--based control of port--Hamiltonian system is then briefly treated, showcasing the popular \textit{energy--balancing} technique. Both theoretical and numerical examples are given. 
%
\newline

%
The latter part of the Chapter deals with hybrid dynamical systems, their \textit{hybrid inclusions} specialization and the basic stability properties of this type of systems. The definition of hybrid inclusion is provided alongside the concept and parametrization of the solutions of this type of models in time domain. Then, an example is provided to consolidate the theory. Finally, the Lyapunov stability theorem for hybrid inclusions is enunciated and applied to the previous examples. 
%

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Chapters/2_1porthamiltonian.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Finally, all the previous results are used to transfer to the hybrid case some of the features of passivity--based control for port--Hamiltonian systems.%%%%%%%%%%%
\input{Chapters/2_2hybridsystems.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
%
In this chapter, the fundamental mathematical tools needed to develop both the theories and applications in the rest of the thesis, have been provided. In particular, stability and passivity of dynamical systems, port--Hamiltonian systems and hybrid systems
%
\newline

%
The next chapter will introduce the theory of hybrid port--Hamiltonian system, a major contribution of this thesis. 

