\chapter*{Research Publications}
\addcontentsline{toc}{chapter}{Research Publications}
\lhead[Research Publications]{}

\thispagestyle{empty}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Peer Reviewed Journal Papers}
\begin{enumerate}[{[}j1{]}]
	\item Jiaxu Wu, Hanwool Woo, Yusuke Tamura, Alessandro Moro, \textbf{Stefano Massaroli},
	Atsushi Yamashita, and Hajime Asama. ``Pedestrian trajectory prediction using BiRNN
	Encoder--Decoder Framework.'' \textit{Advanced Robotics}, 2019.
	%
	\item \textbf{Stefano Massaroli}, Federico Califano, Angela Faragasso, Atsushi Yamashita, and Hajime Asama: ``Port--Hamiltonian approach to asymptotic stabilisation of Lotka--Volterra equations.'', \textit{Nature Communications}, 2019 (To be submitted).
	%
	\item \textbf{Stefano Massaroli}, Federico Califano, Angela Faragasso, Atsushi Yamashita, and Hajime Asama: ``Iterative energy shaping of a ball--dribbling robot.'', \textit{Mechatronics}, 2019 (To be submitted).
\end{enumerate}

\section*{Peer Reviewed Conference Papers}
\begin{enumerate}[{[}c1{]}]
\item \textbf{Stefano Massaroli}, Renato Miyagusuku, Federico Califano, Claudio Melchiorri, Atsushi Yamashita, and Hajime Asama: ``Recursive algebraic Frisch scheme: a particle--based approach'', \textit{Proceedings of the 9th IFAC Symposium of Robust Control}, pp. 409--415, Florianapolis (Brazil), September 2018.
%
\item \textbf{Stefano Massaroli}, Renato Miyagusuku, Federico Califano, Angela Faragasso, Atsushi Yamashita, and Hajime Asama: ``A novel recursive linear estimator based on the Frisch scheme.'', \textit{Proceedings of the 12th Asian Control Conference}, pp. 1106--1011, Kitakyushu (Japan), June 2019.
%
\item \textbf{Stefano Massaroli}, Federico Califano, Angela Faragasso, Atsushi Yamashita, and
Hajime Asama. ``Iterative energy shaping of a ball--dribbling robot." \textit{Proocedings of the 2019 IFAC Workshop on Robot Control}, Daejeon (Korea), September 2019. (Accepted)
%
\item \textbf{Stefano Massaroli}, Michael Poli, Federico Califano, Angela Faragasso, Jinkyoo Park, Atsushi Yamashita, and Hajime Asama: ``Port--Hamiltonian approach to neural network training.'' \textit{Proocedings of the 58th IEEE Control and Decision Conference}, Nice (France), December 2019. (Accepted)
%
\item \textbf{Stefano Massaroli}, Federico Califano, Claudio Melchiorri, Atsushi Yamashita, and Hajime Asama: ``A novel identification procedure for the dynamic parameters of robots based on the Frisch scheme.'' \textit{Proocedings of the 15th IFAC Workshop on Advanced Control and Diagnosis}, Bologna (Italy), November 2019. (Submitted)
%
\item \textbf{Stefano Massaroli}, Federico Califano, Angela Faragasso, Mattia Risiglione, Atsushi
Yamashita, and Hajime Asama. ``Identification of a class of hybrid dynamical systems.'' \textit{2020 IFAC World Congress}, Berlin (Germany), 2019. (To be submitted)
%
\item \textbf{Stefano Massaroli}, Federico Califano, Angela Faragasso, Atsushi Yamashita, and Hajime Asama: ``Multistable energy shaping of linear time--invariant systems with hybrid mode selector.'' \textit{2020 IFAC World Congress}, Berlin (Germany), 2019. (To be submitted)
%
\end{enumerate}

\section*{Poster Presentations}
\begin{enumerate}[{[}p1{]}]
\item \textbf{Stefano Massaroli}, Atsushi Yamashita, and Hajime Asama: ``Hybrid energy--based control of a ball--dribbling robot'', \textit{2019 IEEE/RSJ International Conference on Intelligent Robots and Systems}, Macau (China), November 2019 (Submitted)%,Vancouver, Canada, September 2017.
\end{enumerate}

\section*{Oral Presentations}
\begin{enumerate}[{[}o1{]}]
	\item \textbf{Stefano Massaroli}, Atsushi Yamashita, and Hajime Asama: ``Biologically inspired control of robots for highly dynamic tasks'', Proceedings of the Tsinghua University- the University of Tokyo
	Joint Symposium on Multi-discipline, pp. 95, Beijing, China, March 2018.
\end{enumerate}