\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}
\lhead[Bibliography]{}

\thispagestyle{empty}

\newpage

\begin{mythebibliography}{}
\bibitem[Ballard 1981]{Ballard1981}
\leavevmode \\
Ballard, Dana H.:
\newblock ``Generalizing the Hough transform to detect arbitrary shapes,''
\newblock Pattern recognition 13, no. 2 (1981): 111-122.
\\

\bibitem[Chong 2015]{chong2015}
\leavevmode \\
Chong, T. J., X. J. Tang, C. H. Leng, M. Yogeswaran, O. E. Ng, and Y. Z. Chong:
\newblock `` Sensor technologies and simultaneous localization and mapping (SLAM),''
\newblock Procedia Computer Science, Vol. 76, pp. 174-179, 2015.
\\ 

\bibitem[Diosi 2004]{dios2004}
\leavevmode \\
Diosi, Albert and Lindsay Kleeman:
\newblock ``Advanced sonar and laser range finder fusion for simultaneous localization and mapping,''
\newblock Proceedings of the 2004 IEEE International Conference on Intelligent Robots and Systems (IROS 2004), Vol. 2, pp. 1854-1859, IEEE, 2004.
\\ 
	
\bibitem[Foster 2013]{Foster2013}
\leavevmode \\
Foster, Paul, Zhenghong Sun, Jong Jin Park, and Benjamin Kuipers:
\newblock ``Visagge: Visible angle grid for glass environments,''
\newblock Proceedings of the 2013 IEEE International Conference on Robotics and Automation (ICRA 2013), pp. 2213-2220, IEEE, 2013.
\\ 
 
\bibitem[Giorgio 2007]{Giorgio2007}
\leavevmode \\
Giorgio Grisetti, Cyrill Stachniss, and Wolfram Burgard:
\newblock ``Improved Techniques for Grid Mapping with Rao-Blackwellized Particle Filters,''
\newblock IEEE Transactions on Robotics, Vol. 23, pp. 34-46, IEEE, 2007.
\\ 
 
\bibitem[Hancock 1999]{hancock1999}
\leavevmode \\
Hancock, John A:
\newblock ``Laser intensity-based obstacle detection and tracking,''
\newblock No. AAT 9936886 (UMI order no.). Carnegie Mellon University, 1999.
\\ 

\bibitem[Iwashina 2007]{iwashina2007}
\leavevmode \\
岩科進也, 山下淳, and 金子透:
\newblock ``レーザ・超音波センサ搭載移動ロボットによる透明物体を含む環境における 2 次元グリッド地図生成,''
\newblock 精密工学会画像応用技術専門委員会サマーセミナー 2007 テキスト, 伊豆, pp. 99-102, 2007.
\\ 

\bibitem[Juds 1988]{juds1988}
\leavevmode \\
Juds, Scott:
\newblock ``Photoelectric sensors and controls: selection and application,''
\newblock  Vol. 63. CRC Press, 1988.
\\ 

\bibitem[Nitzan 1977]{nitzan1977}
\leavevmode \\
Nitzan, David, Alfred E. Brain, and Richard O. Duda:
\newblock ``The measurement and use of registered reflectance and range data in scene analysis,''
\newblock  Proceedings of the IEEE Vol. 65, no. 2, pp. 206-220, 1977.
\\ 

\bibitem[Kawata 2005]{kawata2005}
\leavevmode \\
Kawata, Hirohiko, Akihisa Ohya, Shinichi Yuta, Wagle Santosh, and Toshihiro Mori:
\newblock ``Development of ultra-small lightweight optical range sensor system,''
\newblock  Proceedings of the 2005 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2005), pp. 1078-1083, IEEE, 2005.
\\ 

\bibitem[Klank 2011]{klank2011}
\leavevmode \\
Klank, Ulrich, Daniel Carton, and Michael Beetz:
\newblock ``Transparent object detection and reconstruction on a mobile platform,''
\newblock Proceedings of the 2013 IEEE International Conference on Robotics and Automation (ICRA 2011), pp. 5971-5978, IEEE, 2011.
\\ 

\bibitem[Kim 2016]{kim2016localization}
\leavevmode \\
Kim, Jiwoong, and Woojin Chung:
\newblock ``Localization of a mobile robot using a laser range finder in a glass-walled environment,''
\newblock IEEE Transactions on Industrial Electronics, Vol. 63, no. 6, pp. 3616-3627, IEEE, 2016.
\\ 
 
\bibitem[Kirchner 2009]{kirchner2009}
\leavevmode \\
Kirchner, Nathan, Dikai Liu, and Gamini Dissanayake:
\newblock ``Surface type classification with a laser range finder,''
\newblock IEEE Sensors Journal, Vol. 9, no. 9, pp. 1160-1168, IEEE, 2009.
\\ 

%\bibitem[Kirchner 2007]{kirchner2007}
%\leavevmode \\
%Kirchner, N. G., T. Taha, D. Liu, and G. Paul:
%\newblock ``Simultaneous material type classification and mapping data acquisition using a laser range finder,''
%\newblock Proceedings of the International Conference on Intelligent Technologies, 2007.
%\\ 

\bibitem[Koch 2017]{koch2017}
\leavevmode \\
Koch, Rainer, Stefan May, Patrick Murmann, and Andreas Nüchter:
\newblock ``Identification of transparent and specular reflective material in laser scans to discriminate affected measurements for faultless robotic SLAM,''
\newblock Robotics and Autonomous Systems, Vol. 87, pp. 296-312, 2017.
\\ 

\bibitem[Pedregosa 2011]{pedregosa2011}
\leavevmode \\
Pedregosa, Fabian, Gaël Varoquaux, Alexandre Gramfort, Vincent Michel, Bertrand Thirion, Olivier Grisel, Mathieu Blondel et al:
\newblock ``Scikit-learn: Machine learning in Python,''
\newblock Journal of Machine Learning Research, Vol. 12, pp. 2825-2830, 2011.
\\ 

\bibitem[Pedrotti 2017]{pedrotti2017}
\leavevmode \\
Pedrotti, Frank L., Leno M. Pedrotti, and Leno S. Pedrotti:
\newblock Introduction to Optics,
\newblock Cambridge University Press, 2017.
\\ 

\bibitem[Qing 2007]{qing2007}
\leavevmode \\
Qing, Zhaoshen, Baoping Ji, and Manuela Zude:
\newblock ``Predicting soluble solid content and firmness in apple fruit by means of laser light backscattering image analysis,''
\newblock Journal of Food Engineering 82, no. 1, pp. 58-67, 2007.
\\ 

\bibitem[Quigley 2009]{quigley2009}
\leavevmode \\
Quigley, Morgan, Ken Conley, Brian Gerkey, Josh Faust, Tully Foote, Jeremy Leibs, Rob Wheeler, and Andrew Y. Ng.:
\newblock ``ROS: an open-source Robot Operating System,''
\newblock In ICRA Workshop on Open Source Software, Vol. 3, no. 3.2, pp. 5, 2009.
\\ 

\bibitem[Ragheb 2002]{ragheb2002}
\leavevmode \\
Ragheb, Hossein, and Edwin R. Hancock:
\newblock ``Lambertian reflectance correction for rough and shiny surfaces,''
\newblock Proceedings of the 2002 International Conference on Image Processing, Vol. 2, pp. II-II, IEEE, 2002.
\\ 
 
\bibitem[Suykens 1999]{suykens1999}
\leavevmode \\
Suykens, Johan AK, and Joos Vandewalle:
\newblock ``Least squares support vector machine classifiers,''
\newblock Neural Processing Letters 9, no. 3, pp. 293-300, 1999.
\\ 

\bibitem[Tanaka 2012]{tanaka2012}
\leavevmode \\
Tanaka, Masahiro, and Keisuke Kochi:
\newblock ``Global localization of a mobile robot with a laser range scanner in the outdoor environment,''
\newblock Proceedings of the 2012 International Conference on Advanced Mechatronic Systems (ICAMechS 2012), pp. 69-74, IEEE, 2012.
\\ 

\bibitem[Thrun 2005]{thrun2005}
\leavevmode \\
Thrun, Sebastian, Wolfram Burgard, and Dieter Fox:
\newblock ``Probabilistic robotics,''
\newblock MIT press, 2005.
\\ 

\bibitem[Wang 2017]{wang2017}
\leavevmode \\
Wang, Xun, and JianGuo Wang:
\newblock ``Detecting glass in simultaneous localisation and mapping,''
\newblock Robotics and Autonomous Systems, Vol. 88, pp. 97-103, 2017.
\\ 

\bibitem[Zhang 2014]{zhang2014}
\leavevmode \\
Zhang, T., Z. J. Chong, B. Qin, J. G. M. Fu, S. Pendleton, and M. H. Ang:
\newblock ``Sensor fusion for localization, mapping and navigation in an indoor environment,''
\newblock Proceedings of the 2014 IEEE International Conference in Humanoid, Nanotechnology, Information Technology, Communication and Control, Environment and Management (HNICEM 2014), pp. 1-6, IEEE, 2014.
\\ 

% 
%\bibitem[Anderson 2002]{anderson2002building}
%\leavevmode \\
%Christopher~R Anderson, Theodore~S Rappaport, Kyung Bae, Alex Verstak, Naren  Ramakrishnan, William~H Tranter, Clifford Shaffer, Layne~T Watson, et~al:
%\newblock ``In-building wideband multipath characteristics at 2.5 and 60 ghz,''
%\newblock In \emph{Vehicular Technology Conference, 2002. Proceedings. VTC  2002-Fall. 2002 IEEE 56th}, volume~1, pages 97--101. IEEE, 2002.
%\\ 
% 
%\bibitem[Astr{\"o}m 2010]{astrom2010feedback}
%\leavevmode \\
%Karl~Johan Astr{\"o}m and Richard~M Murray:
%\newblock ``\emph{Feedback systems: an introduction for scientists and  engineers},''
%\newblock Princeton university press, 2010.
%\\ 

\end{mythebibliography}

