\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\lhead[Acknowledgements]{}

\thispagestyle{empty}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As this thesis concludes, I would like to acknowledge and thank the guidance, cooperation and support of all the people who have helped my throughout the completion of this thesis.

I would like to start by expressing my utmost gratitude towards my supervisor, professor Atsushi Yamashita, for giving me the chance to be part of his research group. I also want to thank him for his constant guidance and support on all aspects of academic research. Specially for the many insightful comments and suggestions that I have received during our regular meetings. All of which have shaped not only this thesis but also my approach towards research in general. 

I am also thankful to the member of my thesis committee, professor Yasushi Umeda, for the time spent reading this thesis, his precise and accurate comments, and keen suggestions into how to improve this work.

Special thanks to professor Hajime Asama, who together with professor Atsushi Yamashita, have always guided me since my arrival to Japan. My utmost thanks for always sparing some time to guide me and for all the the wise comments and suggestion I have always received. 

I would like to also thank assistant professor Qi An, who has always helped me in several ways since my arrival to Japan. Thank to Dr. Alessandro Moro and Dr. Angela Faragasso, for their insightful and helpful suggestions on my research. Also many thanks to Dr. Hiroshi Yamakawa for helping me in all hardware related requirements I have had.

I would like to extend my thanks to my seniors, specially to Mr. Renato Miyagusuku, on whose extensive knowledge in SLAM and related areas I have always relied on, as well as for always willingly helping me in the operation of robot, lab related procedures, researching life in general. Special thanks also to Dr. Sarthak Pathak, for all his comments and suggestions on my work, all the time he invested in reviewing this thesis, as well as the numerous witty jokes he shared with me. 

I would also like to extend my thanks to everyone at the Asama-Yamashita lab, specially to everyone at the robotics' related group. In particular, many thanks to Mr. Hiroshi Higuchi for all the insightful comments and suggestions on my work, and for all the time spent reviewing this thesis. Also, special thanks to Mr. Younes Louhi, Mr. Ren Komatsu, Ms. Ningjia Yang, as well as former members Mr. Binbin Xu and Mr. Yuyang Shao for all research and non-research related discussions. Many thanks to former member Ms. Wei Sun, who was my tutors since my arrival to Japan. Thanks for helping me with the documents inside and outside the university. 

Thanks to Ms. Rika Kojima, Ms. Megumi Nakamura, and special thanks to Ms. Hisae Narushima for always helping me, and everyone at the laboratory, in all administrative matters. Their counsel and prompt replies have been a great help these two years. 

I also want to extend my thanks to the Iwatani Naoji Foundation for awarding me with the International Student Scholarship. Without their help, carrying my studies in Japan and the development of this thesis would not have been possible.

In addition, I would like to thank my friends, those in my home country China and those I have made in Tokyo, for their help and support to my master study. Special thank to Ms. Yao Liu, who is my roommate in Tokyo and also one of my best friends, for the pleasant time we spent together and the meaningful conservations we had in our small house.  

At the end, most importantly I would like to thank to my family, especially my parents, for their continuous and relentless support, which has made my live these last years so much more pleasurable.

To all, thank you very much.

\begin{flushright}
July 2018 \enspace Jun Jiang
\end{flushright}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Local Variables:
%%% mode: katex
%%% TeX-master: "../thesis"
%%% End:
